Analysis of Tick-Bourne Disease Cases Reported to DPH Between 2019-2024

### 2025-04-21 code/processing-code/processing-code-tickcases.qmd
Update
Reviewer - I need help with why on Docx my numbering gets all weird -- the numbering looks fine on my end on R

# Create histogram of disease counts
disease_histogram <- ggplot(cleaned_data3, aes(x = DISEASE)) +
  geom_bar(fill = "#2C3E50", color = "white") +  # Dark blue bars with white edges
  theme_minimal() +
  labs(
    title = "Distribution of Tick-Bourne Disease\nTypes for Confirmed Cases in Georgia (2019-2024)",
    x = "Disease Type",
    y = "Count"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 10),  # Rotate & reduce x-axis label size
    plot.title = element_text(hjust = 0.5, face = "bold", size = 14),
    plot.margin = margin(10, 10, 20, 10)  # Adjust margins to prevent cutoff
  )

@@

# Save the plot
ggsave(filename = save_plot_location, plot = disease_histogram, width = 12, height = 6, dpi = 300)
```

>>>>

# Create histogram of disease counts
disease_plot <- ggplot(cleaned_data3, aes(x = DISEASE)) +
  geom_bar(fill = "#2C3E50", color = "white") +  # Dark blue bars with white edges
  theme_minimal() +
  labs(
    title = "Distribution of Tick-Bourne Disease\nTypes for Confirmed Cases in Georgia (2019-2024)",
    x = "Disease Type",
    y = "Count"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 10),  # Rotate & reduce x-axis label size
    plot.title = element_text(hjust = 0.5, face = "bold", size = 14),
    plot.margin = margin(10, 10, 20, 10)  # Adjust margins to prevent cutoff
  )

@@

# Save the plot
ggsave(filename = save_plot_location, plot = disease_plot, width = 12, height = 6, dpi = 300)
```

### 2025-04-21 products/manuscript/Manuscript.qmd
Update
Reviewer - I need help with why on Docx my numbering gets all weird -- the numbering looks fine on my end on R

+-----------------+-----------+-----------+-----------+-----------+
| term            | estimate  | s         | statistic | p.value   |
|                 |           | td.error  |           |           |
| \<chr\>         | \<dbl\>   |           | \<dbl\>   | \<dbl\>   |
|                 |           | \<dbl\>   |           |           |
+:================+==========:+==========:+==========:+==========:+
| ( Intercept)    | -2 3 2    | 1 57      | 1         | 0.1729390 |
|                 | 8.5151515 | 3.052665  | .48025251 |           |
+-----------------+-----------+-----------+-----------+-----------+
| YEAR            | 1.1515152 | 0.777581  | 1         | 0.1727716 |
|                 |           |           | .48089418 |           |
+-----------------+-----------+-----------+-----------+-----------+
| BABESIOSIS      | 0.4242424 | 5.484565  | 0         | 0.9400358 |
|                 |           |           | .07735207 |           |
+-----------------+-----------+-----------+-----------+-----------+
| DENGUE          | 4.8484848 | 6.364775  | 0         | 0.4656907 |
|                 |           |           | .76176850 |           |
+-----------------+-----------+-----------+-----------+-----------+
| EHRLICHIA       | 5.0000000 | 5.157889  | 0         | 0.3576794 |
| CHAFFEENSIS     |           |           | .96938889 |           |
+-----------------+-----------+-----------+-----------+-----------+
| EHRLICHIA       | -         | 6.364775  | 0         | 0.8604390 |
| EWINGII         | 1.1515152 |           | .18092002 |           |
+-----------------+-----------+-----------+-----------+-----------+
| LYME DISEASE    | 8.5606061 | 4.963745  | 1         | 0.1186814 |
|                 |           |           | .72462659 |           |
+-----------------+-----------+-----------+-----------+-----------+
| ROCKY MOUNTAIN  | 0.5757576 | 5.484565  | 0         | 0.9186958 |
| SPOTTED FEVER   |           |           | .10497781 |           |
+-----------------+-----------+-----------+-----------+-----------+
| WEST NILE (WNV) | 8.2272727 | 5.593721  | 1         | 0.1754208 |
| INFECTION       |           |           | .47080497 |           |
+-----------------+-----------+-----------+-----------+-----------+

@@

+----------+----------+----------+----------+----------+
| term     | estimate | s        | s        | p.value  |
|          |          | td.error | tatistic |          |
| \<chr\>  | \<dbl\>  |          |          | \<dbl\>  |
|          |          | \<dbl\>  | \<dbl\>  |          |
+:=========+=========:+=========:+=========:+=========:+
| ( I      | 9 9      | 5 7      | 1.733920 | 0        |
| n        | 3        | 2        |          | .1434648 |
| tercept) | 5.267857 | 9.946482 |          |          |
+----------+----------+----------+----------+----------+
| YEAR     | -        | 2.835202 | -        | 0        |
|          | 4.910714 |          | 1.732051 | .1438108 |
+----------+----------+----------+----------+----------+

@@

+----------------+----------------+----------------+----------------+
|                |                |                |                |
+----------------+----------------+----------------+----------------+
|                |                |                |                |
+----------------+----------------+----------------+----------------+

@@

+----------------+----------------+----------------+----------------+
| Model Type     | Predictors     | Accuracy       | ROC AUC        |
|                | Used           |                |                |
+================+================+================+================+
| Random Forest  | Age, Sex,      | 78.1%          | 0.68           |
|                | County,        |                |                |
|                | Disease        |                |                |
+----------------+----------------+----------------+----------------+
| Random         | Poverty Rate   | 88.4%          | 0.46           |
| Forest -       | By County      |                |                |
| Poverty Rate   |                |                |                |
| Only           |                |                |                |
+----------------+----------------+----------------+----------------+

>>>>

+-----------+-----------+-----------+-----------+-----------+
| term      | estimate  | s         | statistic | p.value   |
|           |           | td.error  |           |           |
| \<chr\>   | \<dbl\>   |           | \<dbl\>   | \<dbl\>   |
|           |           | \<dbl\>   |           |           |
+:==========+==========:+==========:+==========:+==========:+
| (         | -2 3 2    | 1 57      | 1         | 0.1729390 |
| I         | 8.5151515 | 3.052665  | .48025251 |           |
| ntercept) |           |           |           |           |
+-----------+-----------+-----------+-----------+-----------+
| YEAR      | 1.1515152 | 0.777581  | 1         | 0.1727716 |
|           |           |           | .48089418 |           |
+-----------+-----------+-----------+-----------+-----------+
| B         | 0.4242424 | 5.484565  | 0         | 0.9400358 |
| ABESIOSIS |           |           | .07735207 |           |
+-----------+-----------+-----------+-----------+-----------+
| DENGUE    | 4.8484848 | 6.364775  | 0         | 0.4656907 |
|           |           |           | .76176850 |           |
+-----------+-----------+-----------+-----------+-----------+
| EHRLICHIA | 5.0000000 | 5.157889  | 0         | 0.3576794 |
| C         |           |           | .96938889 |           |
| H         |           |           |           |           |
| AFFEENSIS |           |           |           |           |
+-----------+-----------+-----------+-----------+-----------+
| EHRLICHIA | -         | 6.364775  | 0         | 0.8604390 |
| EWINGII   | 1.1515152 |           | .18092002 |           |
+-----------+-----------+-----------+-----------+-----------+
| LYME      | 8.5606061 | 4.963745  | 1         | 0.1186814 |
| DISEASE   |           |           | .72462659 |           |
+-----------+-----------+-----------+-----------+-----------+
| ROCKY     | 0.5757576 | 5.484565  | 0         | 0.9186958 |
| MOUNTAIN  |           |           | .10497781 |           |
| SPOTTED   |           |           |           |           |
| FEVER     |           |           |           |           |
+-----------+-----------+-----------+-----------+-----------+
| WEST NILE | 8.2272727 | 5.593721  | 1         | 0.1754208 |
| (WNV)     |           |           | .47080497 |           |
| INFECTION |           |           |           |           |
+-----------+-----------+-----------+-----------+-----------+

@@

+--------+--------+--------+--------+--------+
| term   | e      | s t    | s t    | p      |
|        | s      | d      | a      | .value |
| \      | timate | .error | tistic |        |
| <chr\> |        |        |        | \      |
|        | \      | \      | \      | <dbl\> |
|        | <dbl\> | <dbl\> | <dbl\> |        |
+:=======+=======:+=======:+=======:+=======:+
| ( I n  | 9 9 3  | 5 7 2  | 1      | 0 .    |
| t      | 5      | 9      | .      | 1      |
| e      | .      | .      | 733920 | 434648 |
| rcept) | 267857 | 946482 |        |        |
+--------+--------+--------+--------+--------+
| YEAR   | -   4  | 2      | -   1  | 0 .    |
|        |     .  | .      |     .  | 1      |
|        | 910714 | 835202 | 732051 | 438108 |
+--------+--------+--------+--------+--------+

@@

+--------------+--------------+--------------+--------------+
|              |              |              |              |
+--------------+--------------+--------------+--------------+
|              |              |              |              |
+--------------+--------------+--------------+--------------+

@@

+--------------+--------------+--------------+--------------+
| Model Type   | Predictors   | Accuracy     | ROC AUC      |
|              | Used         |              |              |
+==============+==============+==============+==============+
| Random       | Age, Sex,    | 78.1%        | 0.68         |
| Forest       | County,      |              |              |
|              | Disease      |              |              |
+--------------+--------------+--------------+--------------+
| Random       | Poverty Rate | 88.4%        | 0.46         |
| Forest -     | By County    |              |              |
| Poverty Rate |              |              |              |
| Only         |              |              |              |
+--------------+--------------+--------------+--------------+
